# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r echo=TRUE}
library(data.table)
setwd("e:\\5")
data <- as.data.table(read.csv("activity.csv"))

ii <- which(is.na(data$steps))
data.zeroed <- data
data.zeroed <- data.zeroed[-ii]
```

## What is mean total number of steps taken per day?

```{r echo=TRUE}
totals <- data.zeroed[,sum(steps),by=date]
hist(totals$V1)
mean(totals$V1)
median(totals$V1)
```

## What is the average daily activity pattern?

```{r echo=TRUE}
data.zeroed <- data
data.zeroed$steps[ii] <- 0
avg.values <- data.zeroed[,mean(steps),by=interval]
plot(avg.values$V1, type='l')
which.max(avg.values$V1)
```

## Imputing missing values

For imputing just write zero value:

```{r echo=TRUE}
ii <- which(is.na(data$steps))
length(ii)

data.imputed <- data
data.imputed[ii]$steps <- 0


totals <- data.imputed[,sum(steps),by=date]
hist(totals$V1)
mean(totals$V1)
median(totals$V1)
```

We can seethat mean & median values differ from the estimates from the first part of the assignment.


## Are there differences in activity patterns between weekdays and weekends?




